Executive Constraints and Civil Conflict Onset

### 2020-01-16 paper.Rmd
Switch to cmdstanr and add simulated data plots

[//]: # Setup R environment for entire doc
```{r include = F, results = "hide"}
knitr::opts_chunk$set(echo = F, eval = F)

library(dplyr)
library(thesis.utils)
```

@@

```{r}
beta <- readRDS("posteriors/summary/beta.rds")
plot_pars(beta)
```

```{r}
input.df <- readRDS("posteriors/input_data.rds")
p_hat <- readRDS("posteriors/summary/predicted_probs.rds")

@@

```{r}
p <- apply(p_hat, 2, median)
x <- evalmod(scores = p, labels = input.df$lepisode_onset)
plot(x, curvetype = c("ROC", "PRC"))
```

@@

```{stan, code = readLines("stan/model.stan"), eval = FALSE, output.var = "x", echo = T}
```

@@

>>>>

[//]: # Setup R environment for entire doc
```{r include = F, results = "hide"}
knitr::opts_chunk$set(echo = F, eval = T)

library(dplyr)
library(ggplot2)
library(gridExtra)
library(thesis.utils)
```

@@

```{r eval = F}
beta <- readRDS("posteriors/summary/beta.rds")
plot_pars(beta)
```

```{r eval = F}
input.df <- readRDS("posteriors/input_data.rds")
p_hat <- readRDS("posteriors/summary/predicted_probs.rds")

@@

```{r eval = F}
p <- apply(p_hat, 2, median)
x <- evalmod(scores = p, labels = input.df$lepisode_onset)
plot(x, curvetype = c("ROC", "PRC"))
```

@@

```{stan, code = readLines("stan/model.stan"), eval = F, output.var = "x", echo = T}
```

@@

In order

```{r}
prior_plot <- function(range, fn, ...) {
    data.frame(x = range) %>%
        ggplot(aes(x)) +
        stat_function(fun = fn, ...)
}

p1 <- prior_plot(c(-20, 20), dnorm, args = list(mean = 0, sd = 5))
p2 <- prior_plot(c(-10, 10), dnorm, args = list(mean = 0, sd = 2.5))
p3 <- prior_plot(c(0, 5), dlnorm, args = list(meanlog = 0, sdlog = 0.5))
p4 <- prior_plot(c(0, 2), dweibull, args = list(shape = 5, scale = 1))
p5 <- prior_plot(c(0, 10), dhcauchy, args = list(sigma = 1))
p6 <- prior_plot(c(0, 5), dgamma, args = list(shape = 5, rate = 5))

grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2, nrow = 3)

```{r warning = F}
pars.df <- readRDS("posteriors/sim/parameters.rds")
ggplot(pars.df, aes(parameter, point, color = type)) +
    geom_point() +
    geom_errorbar(aes(parameter, ymin = codelow, ymax = codehigh),
                  width = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

```{r warning = F}
latent <- readRDS("posteriors/sim/theta.rds") %>%
    arrange(true_value) %>%
    mutate(idx = 1:n())

ggplot(latent, aes(idx, true_value)) +
    geom_point(col = "darkgrey") +
    geom_errorbar(aes(ymin = codelow, ymax = codehigh), alpha = 0.2, col = "darkblue") +
    ylab("True Value") +
    theme(axis.text.x = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks.x = element_blank())
```

```{r results = 'hide'}
x <- with(latent, mean(true_value <= codehigh & true_value >= codelow))
```

hello world `r x * 100`%
